Agda Meets Accelerate

### 2012-07-31 paper/main.tex
More in the introduction

Dependent types are an emerging approach to certified programming,
where invariants are established and proved at compile time.

Thus, it seems fruitful to explore the potential of dependent types in
the context of data-parallel prorgamming.

>>>>

Dependent types are an emerging approach to certified programming, where invariants are established in the form of types and proved at compile time. Many of Haskell's type-level extensions used in Accelerate approximate various aspects of dependently-typed programming. Hence, it it is natural to ask whether fully-fledged dependent types, such as those provided by Agda, improve the specification of an embedded language like Accelerate, whether they increase the scope of static guarantees, and whether they may be leveraged to predict performance more accurately.
